### 2020-03-02 manuscript.tex
Update manuscript.tex

— secondary analysis/socio demographic —

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community). Modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.

Modernization (e.g., education and high socioeconomic status) had no clear impact on the likelihood of FGC, but education plays an important role in the mother's decision not to circumcise her daughter as in Nigeria \cite{KandNwak09}. Our findings also showed that education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation.  While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}.

While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had not clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.  Individual education also found a positive correlation in discontinuation of FGC, such as in Egypt \cite{DalaLawo10, VanMeek16}.  Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, as found in Ethiopia \cite{MashMatt09}

@@

———— stop reading —————
=========
% education:  \cite{DalaLawo10, KandNwak09, PashPonn16, VanMeek1};

% age\cite{PashPonn16, SipsChen12},

>>>>

— socio demographic factors —

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).

The positive impact modernization \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02} on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded \cite{Hayf05} \cfonly{to confirm}. While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.

Regarding FGC continuity, education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation in our findings.  While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}, and to Egpyt \cite{DalaLawo10, VanMeek16}. A secondary analysis of the Egypt DHS from 1995 to 2014 showed a positive correlation of individual level of education, job and wealth with their attitudes of FGC continuity \cite{VanMeek15} .

@@

———— stop reading —————
=========
